---
title: "Final Project"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Final Project}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FinalProject)
```
#Introduction 

##Constructor Function. What data set we are using and how to. 
##Print Function 
##The var.test(x,y) will compare the two variances. Ho: alpha2^2/alpha1^2 = 1
##We measure this for the P Value. From the output we see a pvalue. Take 0.05 and compare. If less than 0.05 we will reject the Null. If greater than 0.05, we will fail to reject. 
##The ttest takes the pvalue and uses it as evidence against the NULL hypothesis. Ho: mu2-mu1 =0. If less than 0.05, we will reject the null. The confidence interval gives upper and lower bounds of the estimate of the difference. 
##tp is the paired ttest. There is no need to worry about variances since there is one sample of differences. 
